\documentclass[a4paper]{article}
\usepackage{amsmath} 
\usepackage{amsfonts}
\usepackage[shortlabels]{enumitem}
\begin{document}  
\title{Mathematics Examination}
\date{DD-MM-YYYY}
\author{Rujuta Budke}
\maketitle
\pagenumbering{gobble}
\newpage

\begin{Large}
\underline{Instructions:}\\
\end{Large}


\noindent \textbf{Duration: 2hrs} \hfill \textbf{Time: 2hrs}
\begin{enumerate}
\item Write your MIS number on paper 
\item Unless otherwise mentioned symbols and notations have their usual standard meaning
\item Use of any kind of electronic device is NOT allowed
\item Any essential result, formula or theorem assumed for answering of questions must be clearly stated.
\end{enumerate}



\pagebreak

\section{Logical Reasoning}
\subsection*{Question I}
1. Establish the logical equivalence, where \textit{x} does not occur as a free variable in A. Assume that domain is non-empty. \hfill [CO3][{\bf 1}]
\begin{center}
$ \forall x (A \implies P(x))\equiv \forall x (A \lor P(x))$
\end{center}

2. Find the conjunction of the propositions \textit{p} and \textit{q} where \textit{p} is the proposition "Rebecca's PC has more than 16GB free hard disk space" and \textit{q} is the proposition "The processor in Rebecca's PC runs faster than 1 GHz'"\hfill [CO1][{\bf 1}]

\subsection*{Question II}
1. Let \textit{p} and \textit{q} be the propositions "The election is decided" and "The votes have been counted," respectively. Express each of the following compound propositions as an English sentence. \hfill [CO2][{\bf 2}]
\begin{enumerate}[a)]
\item $\neg p \land q$
\item $ p \iff q $
\end{enumerate} 
2. Determine the truth value of the each of these domains if the domain consists of all real numbers.\hfill [CO2][{\bf 2}]
\begin{enumerate}[a)]
\item $\exists x (x^3 = -1) $
\item $\forall x((-x)^2 = x^2)$
\end{enumerate} 


\newpage
\section{Algebra}
\subsection*{Question I}
1. Find eigenvalues and corresponding eigenvectors of A = 
	$\begin{bmatrix}
	2 & -1 \\ -1 & 2
	\end{bmatrix}$. Hence, find an orthogonal basis for $ \mathbb{R} ^2$
	\hfill [CO2][{\bf 2}]\\ \\
2. Find the rank of matrix $
	\begin{bmatrix}
	8 & 6 & 4 & 1 & 3\\
	2 & 1 & -7 & 4 & 1\\	
	1 & 1 & -1 & 2 & 1\\
	1 & -1 & 2 & 0 & 0\\
	\end{bmatrix}$ 
	\hfill [CO3][{\bf 3}]
\subsection*{Question II}
1. Determine whether $\lbrace 1, x^2, x^2 + 2 \rbrace$ spans $P_2(\mathbb{R})$. Is it linearly independent? Justify your answers.\hfill [CO4][{\bf 1}]\\ \\
2. Let V be a vector space. Prove that $W_1$ and $W_2$  are subspaces of V then their intersection $W_1 \cup W_2$ is a subspace of V.\hfill [CO2][{\bf 2}]
\newpage
\section{Calculus}
\subsection*{Question I}
%nested lists
\begin{enumerate}
\item Attempt the following questions:
	\begin{enumerate}[a)]
	\item Find the particular solution of the initial value problem: \hfill [CO2][{\bf 2}]
	
		\begin{align*}
	\tan x\frac{dy}{dx}&=y
	\\y(\frac{\pi}{2})&=(\frac{\pi}{2})
		\end{align*} 
	
	\item Check the whether the following differential equation is exact or non-exact and justify your answer.\hfill [CO2][{\bf 2}]
	 	\begin{equation*}
	 (1 + \ln xy)dx + (1 + \frac{x}{y})dy = 0
		\end{equation*} 
	\end{enumerate}
\item Find a second order homogeneous LDE for which following are LI solutions: $ e^{-kx}\cos {\pi x}, e^{-kx}\sin {\pi x} $ \hfill [CO3][{\bf 2}]
\end{enumerate}

\subsection*{Question II}
\begin{enumerate}
\item Solve using variation of parameters\hfill [CO3][{\bf 4}]
	\begin{enumerate}[i)]
	\item $ y'' + 4y = \cos{2x} $
	\item $(D^2 + 2D + 2I)y = 4e^{-x} \sec^3 x $
	\end{enumerate}
\item Solve the following non-homogeneous LDE using the method of undetermined coefficients:\hfill [CO5][{\bf 4}]
	\begin{enumerate}[i)]
	\item $y'' - 4y' = 8 \cos {\pi x}$
	\item $(D^2 - I)y = \sinh x $
	\end{enumerate}
\item Solve: $ \int \frac{x}{x(x+1)(x+2)} \ dx $\hfill [CO3][{\bf 2}]
\end{enumerate}
\end{document}  

